\chapter{Introduction} \label{section:introduction}

Object tracking is a core problem in computer vision because it connects per-frame detection 
with temporal reasoning over a video sequence. In practical systems, the tracker must not only 
estimate object motion but also operate within clear constraints on latency, memory, and hardware 
cost. This project addresses that setting by building a single-object, SORT-inspired tracking 
pipeline that can be validated in software and represented in a hardware-friendly form.

The literature review showed that tracking-by-detection methods remain effective when the scene 
is dominated by a visible foreground object and when the implementation is designed around 
lightweight state estimation. Background subtraction offers a practical way to isolate moving 
regions, while Kalman-based tracking and IoU gating provide a compact prediction-update framework. 
However, many existing approaches either focus only on software performance or add complexity that 
is not ideal for hardware mapping. This project positions itself between those two extremes by 
keeping the model simple, deterministic, and suitable for fixed-point implementation.

\section{Project Definition}
\label{section:proj_def}
The project implements a foreground-driven object tracker for a single dominant target in video. 
Each frame is processed to extract a bounding box, the box is converted into the SORT state 
representation, and the tracker then predicts and updates the state using a constant-velocity 
model. A Verilog controller mirrors the same logic in hardware-oriented form so that the software 
reference and hardware flow can be compared on the same input stream.

The report therefore covers four connected parts: detection, state representation, prediction and 
update logic, and validation against reference outputs. Together, these steps provide a compact 
end-to-end workflow for evaluating a tracking system that is both computationally lightweight and 
implementation-aware.

\section{Project Objectives}
\label{section:proj_obj}
The objectives of the project are:
\begin{enumerate}
\item To design a foreground-based detection pipeline that converts video frames into stable bounding boxes.
\item To implement a SORT-style tracking model with constant-velocity prediction and IoU-based association.
\item To express the state, covariance, and noise terms in compact fixed-point formats suitable for hardware.
\item To map the tracking logic into a Verilog controller that separates datapath and control behavior.
\item To compare the custom implementation with a Python reference flow and evaluate the alignment between them.
\end{enumerate}

These objectives guided the development of the methodology and the validation of the final results. The 
report shows that the tuned configuration is able to track the target more consistently than the untuned 
baseline, while also highlighting the sensitivity of the system to detector stability and parameter choice.